

```{r}
data <- read_csv("../data/ignite_afterschool/MSS22_Race_NoCounty/MSS22-3RaceNoCounty+Region.csv")
```

## Wrangling
Assume that after school active students are like this again:
that all of the following counts as afterschool activities:
- I stay at my school or go to another school \
- My home or another home such as a friend's, relative's or neighbor's \
- A rec, community or other youth center \
- A park or other outdoor space \
- A library \
- A church, synagogue, mosque, or other spiritual/religious place \ 

These are A34A, A34B, A34C,.. A34F at scale more than 3 in the table.
afterschool = if_else(A34A > 3 | A34B > 3 | A34C > 3 | A34D > 3 | A34E > 3 | A34F > 3, TRUE, FALSE)


```{r}
data <- data %>% mutate(
    # Replace NA values with 0
    across(starts_with("A34"), ~replace_na(., 0)),
    # Calculate afterschool based on conditions
    afterschool = if_else(A34A > 3 | A34B > 3 | A34C > 3 | A34D > 3 | A34E > 3 | A34F > 3, TRUE, FALSE)
)

```

By Race/Ethnicity, 
A3G - 0/1, 1 means white, 0 means youth of color \
A5E - Hmong \
A6F - Somali\

```{r}
main_data <- data %>% select(A34A, A34B, A34C, A34D, A34E, A34F,A3G, A5E, A6F, afterschool)

main_data %>% head()
```

```{r}
race_report <- function(col, name, edge_case_youth_color= FALSE) {
  val=1
  if (edge_case_youth_color) { 
    val = 0
    col = `A3G`
  }
  report<- data %>% 
    filter(A3G == val) %>% 
    summarize(
      name=name,
      count_afterschool_active = sum(afterschool == TRUE),
      count_afterschool_not_active = sum(afterschool == FALSE)
    )
  return (report)
}
```

```{r}
race_report(A3G, "white")
race_report(A3G, "w", edge_case_youth_color = TRUE)
race_report(A3G, "white")
race_report(A3G, "white")
```

