# Race Ethnicity Updating Brief (Ongoing)

```{r}
library(tidyverse)
```

```{r}
source("Wrangling.r")
```

```{r}
data <- read_csv("../data/ignite_afterschool/MSS22_Race_NoCounty/MSS22-3RaceNoCounty+Region.csv")
```


## Wrangling
Assume that after school active students are like this again:
that all of the following counts as afterschool activities:
- I stay at my school or go to another school \
- My home or another home such as a friend's, relative's or neighbor's \
- A rec, community or other youth center \
- A park or other outdoor space \
- A library \
- A church, synagogue, mosque, or other spiritual/religious place \ 

These are A34A, A34B, A34C,.. A34F at scale more than 3 in the table.
afterschool = if_else(A34A > 3 | A34B > 3 | A34C > 3 | A34D > 3 | A34E > 3 | A34F > 3, TRUE, FALSE)

```{r}
A34 <- data %>%
  select(Region, A34A, A34B, A34C, A34D, A34D, A34E, A34F, `A3G`, `A5E`, `A3A`)
```

Also it is important to note that the region is only either 1 (7-County Twin Cities Metro Area) or 2 (Greater Minnesota). It can be (0) undefined too.

A3G White youth
5E. If you are Asian, South Asian or Asian American, which group best describes you? (If more than one describes you, Mark ALL that apply) - Hmong
3A. How do you describe yourself? (Mark ALL that apply) - American Indian or Alaskan Native
Youth of color = all - white
```{r}
report <- A34 %>%
  group_by(Region) %>%
  mutate(
    across(starts_with("A34"), ~replace_na(., 0)),
    afterschool = if_else(A34A > 3 | A34B > 3 | A34C > 3 | A34D > 3 | A34E > 3 | A34F > 3, TRUE, FALSE)
  ) %>% 
  summarize(
    hmong = count(A5E == 1 && afterschool == TRUE) / count(A5E == 1)
  )

```
```{r}
report <- report %>% select(Region, afterschool, `A3G`, `A5E`, `A3A`)
```

```{r}
report %>%  
```


```{r}
count_occurrences(report$A5E)
```


