# Race Ethnicity Updating Brief (Ongoing)

```{r}
library(tidyverse)
```


```{r}
data <- read_csv("../data/ignite_afterschool/MSS22_Race_NoCounty/MSS22-3RaceNoCounty+Region.csv")
```

## Wrangling
Assume that after school active students are like this again:
that all of the following counts as afterschool activities:
- I stay at my school or go to another school \
- My home or another home such as a friend's, relative's or neighbor's \
- A rec, community or other youth center \
- A park or other outdoor space \
- A library \
- A church, synagogue, mosque, or other spiritual/religious place \ 

These are A34A, A34B, A34C,.. A34F at scale more than 3 in the table.
afterschool = if_else(A34A > 3 | A34B > 3 | A34C > 3 | A34D > 3 | A34E > 3 | A34F > 3, TRUE, FALSE)


```{r}
data <- data %>% mutate(
    # Replace NA values with 0
    across(starts_with("A34"), ~replace_na(., 0)),
    # Calculate afterschool based on conditions
    afterschool = if_else(A34A > 3 | A34B > 3 | A34C > 3 | A34D > 3 | A34E > 3 | A34F > 3, TRUE, FALSE)
)
county_code <- read_csv("complete_county_dict.csv")
data <- data %>% left_join( county_code, 
           by=c('County'='Code'))



```



By Race/Ethnicity, 
A3G - 0/1, 1 means white, 0 means youth of color \
A5E - Hmong \
A6F - Somali\

```{r}
main_data <- data %>% select(A34A, A34B, A34C, A34D, A34E, A34F,A3G, A5E, A6F, afterschool, County)


```

```{r}
race_report <- function(col, name, edge_case_youth_color = FALSE, by_region='all') {
  if (by_region == 'all') {
    val <- 1
    if (edge_case_youth_color) { 
      val <- 0
      col <- data$A3G
    }
    report <- data %>% 
      filter(col == val) %>% 
      summarize(
        name = name,
        count_afterschool_active = sum(afterschool == TRUE),
        count_afterschool_not_active = sum(afterschool == FALSE),
        percentage_afterschool_active = count_afterschool_active / n() * 100,
        percentage_afterschool_not_active = count_afterschool_not_active  / n() * 100
      )
  
  return(report)
  }
  else {
    val <- 1
    if (edge_case_youth_color) { 
      val <- 0
      col <- data$A3G
    }
    report <- data %>% 
      filter(filter(col == val) %>% 
      group_by(Region)
      summarize(
        name = name,
        count_afterschool_active = sum(afterschool == TRUE),
        count_afterschool_not_active = sum(afterschool == FALSE),
        percentage_afterschool_active = count_afterschool_active / n() * 100,
        percentage_afterschool_not_active = count_afterschool_not_active  / n() * 100
      )
  
  return(report)
  }
  
}

```

```{r}
white <-race_report(data$A3G, "White")
color<-race_report(data$A3G, "Color", edge_case_youth_color = TRUE)
hmong <- race_report(data$A5E, "Hmong")
race_report(data$A6F, "Somali")
```

