
# Cannabis

## Research Questions

During the last 12 months, have you used marijuana (pot, weed) or hashish (hash, hash oil) (for grade 5)

During the last 12 months on how many occasions (if any) have you used marijuana or hashish? (Do not count medical marijuana prescribed for you by a doctor) (for grades 8,9,11)

5. How much do you think people risk harming themselves physically or in other ways if they use marijuana once or twice per week grades 8,9,11)


For 2, I'm interested if it can be broken down by race/ethnicity and then by region.
For 3 the same- by race and then by region.  I also wonder about gender identity and if there is anything interesting in that breakdown.
For 5- the same.  By grade and then by race, region and gender identity.

```{r}
library(readr)
library(dplyr)
```

```{r}
race_no_county <- read_csv("../data/ignite_afterschool/MSS22_Race_NoCounty/MSS22-3RaceNoCounty+Region.csv")
```

Race	
  1	American Indian or Alaskan Native only
	2	Asian or Asian American only
	3	Black, African or African American only
	4	Hispanic or Latino/a only
	5	Middle Eastern or North African
	6	Native Hawaiian or Other Pacific Islander only
	7	White only
	8	Multiple Races (checked more than one)
	9	No answer
	
## Question 5 broken down by region
```{r}
data <- read_csv("../data/ignite_afterschool/MSS22-3CountyNoRace/MSS22-3CountyNoRace.csv")
county_code <- read_csv("../code/complete_county_dict.csv")
```
```{r}
main <- data %>% left_join( county_code, 
           by=c('County'='Code'))

main
```





```{r}
data2 <- main %>% select(Region, biosex, A100A, A92)
```

```{r}

# Define the function
summarize_q5<- function(data, column) {
  res <- data %>% 
  group_by(!!sym(column)) %>% 
  summarize(
    `No Risk` = paste0(round(sum(A100A == 1, na.rm = TRUE) / n() * 100, 2), "%"),
    `Slight` = paste0(round(sum(A100A == 2, na.rm = TRUE) / n() * 100, 2), "%"),
    `Moderate` = paste0(round(sum(A100A == 3, na.rm = TRUE) / n() * 100, 2), "%"),
    `Great` = paste0(round(sum(A100A == 4, na.rm = TRUE) / n() * 100, 2), "%"),
    `NA` = paste0(round(sum(is.na(A100A)) / n() * 100, 2), "%")
  )
  return (res)
}
```

```{r}
report_5_biosex <- summarize_q5(data2, "biosex")

report_5_region <- summarize_q5(data2, "Region")
```


```{r}
report_5_biosex
report_5_region 
```
biosex 1-3: male, female, no answer

```{r}
report_5_race <- summarize_q5(race_no_county, "Race")
```

```{r}
report_5_race
```


## Question 2

Question 2 cannot be attempted because too many NA data.

## Question 3

```{r}
# Define the function
summarize_q3 <- function(data, column) {
  res <- data %>% 
  group_by(!!sym(column)) %>% 
  summarize(
    `0 time` = paste0(round(sum(A92 == 1, na.rm = TRUE) / n() * 100, 2), "%"),
    `1 to 2` = paste0(round(sum(A92 == 2, na.rm = TRUE) / n() * 100, 2), "%"),
    `3 to 5` = paste0(round(sum(A92 == 3, na.rm = TRUE) / n() * 100, 2), "%"),
    `6 to 9` = paste0(round(sum(A92 == 4, na.rm = TRUE) / n() * 100, 2), "%"),
    `10 to 19` = paste0(round(sum(A92 == 5, na.rm = TRUE) / n() * 100, 2), "%"),
    `20 to 39` = paste0(round(sum(A92 == 6, na.rm = TRUE) / n() * 100, 2), "%"),
    `40 or more` = paste0(round(sum(A92 == 7, na.rm = TRUE) / n() * 100, 2), "%"),
    `NA` = paste0(round(sum(is.na(A92)) / n() * 100, 2), "%")
  )
  return (res)
}
```
```{r}
report_3_region <- summarize_q3(data2, "Region")
```


```{r}
race_no_county %>% head()
```
```{r}
report_3_race <- summarize_q3(race_no_county, "Race")
report_3_race
```

