---
editor_options: 
  markdown: 
    wrap: 72
---

# Update data briefs on engagement after school

## Load libraries and data

```{r}
library(readr)
library(dplyr)
library(readxl)
```

```{r}
county_code <- read_csv("complete_county_dict.csv")
```

```{r}
main <- read_csv("../data/ignite_afterschool/MSS22-3CountyNoRace/MSS22-3CountyNoRace.csv")
```

## Assumption

Use County No Race table MSS22-3CountyNoRace.csv

Assume that all of the following counts as afterschool activities: - I
stay at my school or go to another school\
- My home or another home such as a friend's, relative's or neighbor's\
- A rec, community or other youth center\
- A park or other outdoor space\
- A library\
- A church, synagogue, mosque, or other spiritual/religious place  

These are A34A, A34B, A34C,.. A34F in the table.

Level

1- 0 days

2- 1 day

3- 2 days

4- 3 to 4 days

5- 5 days

## Wrangling

```{r}
# Mutate main by county code
main <- main %>% left_join( county_code, 
           by=c('County'='Code'))

main
```

```{r}
A34 <- main %>%
  select(County, A34A, A34B, A34C, A34D, A34D, A34E, A34F, Region)
```

```{r}
report <- A34 %>%
  group_by(Region) %>%
  mutate(
    across(starts_with("A34"), ~replace_na(., 0)),
    afterschool = if_else(A34A > 3 | A34B > 3 | A34C > 3 | A34D > 3 | A34E > 3 | A34F > 3, TRUE, FALSE)
  ) %>%
  summarise(
    total = n(),
    afterschool_true = sum(afterschool == TRUE, na.rm = TRUE),
    afterschool_false = sum(afterschool == FALSE, na.rm = TRUE),
    afterschool_na = sum(is.na(afterschool)),
    percent_true = afterschool_true / total *100,
    percent_false = afterschool_false / total *100,
    percent_unknown = afterschool_na/ total * 100
  ) 

clean_report <- report %>%
  select(Region, percent_true, percent_false, percent_unknown, total)
```

## Result

These show by region how many youths not regularly active in afterschool
activities (\>= 3 times a week).

```{r}
clean_report
```

```{r}
write_csv(report, "../result/afterschool_x3_report.csv")
write_csv(clean_report, "../result/clean_afterschool_x3_report.csv")
```

## Result 2 (Bonus) - How many respondents make up the youth surveys in a region

```{r}
region_perc <- report %>% 
  
  summarize(
    Region= Region,
    sum = sum(total),
    region_count= total,
    region_perc = total/ sum * 100,
    )

region_perc <- region_perc %>%  select(Region, region_perc, region_count, sum)
```

```{r}
region_perc
```

```{r}
write_csv(region_perc, "../result/region_percent_survey.csv")
```
