---
title: "mental_health_exploration"
format: html
editor: visual
---

## Mental Health

```{r}
library(readr)
library(ggplot2)
library(dplyr)
```


```{r}
main <- read_csv("../data/MSS22-3CountyNoRace/MSS22-3CountyNoRace.csv")
```

23E. What are the reasons you missed a full or part of a day of school in the last 30 days? (Mark ALL that apply) - Felt very sad, hopeless, anxious, stressed or angry
```{r}
main %>% 
  count(A23E)
```

A59A (L2 and L3 only) 59A. Over the past 2 weeks, how often have you been bothered by little interest or pleasure in doing things?
```{r}
main %>% 
  count(A59A)
```

A59B (L2 and L3 only) 59B. Over the past 2 weeks, how often have you been bothered by feeling down, depressed or hopeless?
```{r}
main %>% 
  count(A59B)
    
```


A59C (L2 and L3 only) 59C. Over the past 2 weeks, how often have you been bothered by feeling nervous, anxious or on edge?
```{r}
main %>% 
  count(A59C)
```

A59D (L2 and L3 only) 59D. Over the past 2 weeks, how often have you been bothered by not being able to stop or control worrying?
```{r}
main %>% 
  count(A59D)
```


A71 (L2 and L3 only) 71. Do you live with anyone who is depressed or has any other mental health issues?

A61A (L2 and L3 only) 61A. Have you ever seriously considered attempting suicide? (Mark ALL that apply) - No
```{r}
main %>% 
  count(A61A)
```

A61B (L2 and L3 only) 61B. Have you ever seriously considered attempting suicide? (Mark ALL that apply) - Yes, during the last year
```{r}
main %>% 
  count(A61B)
```


A61C (L2 and L3 only) 61C. Have you ever seriously considered attempting suicide? (Mark ALL that apply) - Yes, more than a year ago
```{r}
main %>% 
  count(A61C)
```


A62A (L2 and L3 only) 62A. Have you ever actually attempted suicide? (Mark ALL that apply) - No
```{r}
main %>% 
 count(A62A)
```

A62B (L2 and L3 only) 62B. Have you ever actually attempted suicide? (Mark ALL that apply) - Yes, during the last year
```{r}
main %>% 
  count(A62B)
```

A62C (L2 and L3 only) 62C. Have you ever actually attempted suicide? (Mark ALL that apply) - Yes, more than a year ago
```{r}
main %>% count(A62C)
```




non cis: A10C, A10A, A10D, A10F, A10G, A10H, A10I, A10J 

A12 (L2 and L3 only) 12. How do you describe your sexual orientation?
1 straight
2 asexual
3 bisexual
4 gay or lesbian
5 questioning/not sure
6 pansexual
7 queer
8 I don’t describe myself in any of these ways
9 I am not sure what this question means 

```{r}
main %>% 
  count(A12)
```

